---
title: "Week 14 IP Anomaly Detection"
author: "Caroline Akoth"
date: "7/28/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Part  $ Anomalies Detection

You have also been requested to check whether there are any anomalies in the given sales dataset. The objective of this task being fraud detection.

## Metric of Success
To successfully perform anomaly detection

## Experimental Design

1. Data Cleaning 
  - Identify and Remove/replace  Missing data
  - Identify and remove duplicate values
  - Removing anomalies
  
2.  Exploratory Data Analysis
  - Univariate, Bivariate and Multivariate Analysis
  
3. Anomaly detection for fraud detection

```{r cars}
# Installing anomalize package
 
install.packages("anomalize")
# Load tidyverse and anomalize
# ---
# 
library(tidyverse)
library(anomalize)
```

```{r}
#Load data
part4 <- read.csv("D:/Education/Self Learning/Data Science/R Tutorials/Week 15 Unsupervised/Supermarket_Sales_Forecasting - Sales.csv")
head(part4)
```
```{r}
# Dimension
dim(part4)
```

## Anomalies Detection

```{r pressure, echo=FALSE}
# Detecting our anomalies
part4 %>%
    time_decompose(count) %>%
    anomalize(remainder) %>%
    time_recompose() %>%
    plot_anomalies(time_recomposed = TRUE, ncol = 3, alpha_dots = 0.5)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
