---
title: "Week 15 IP - Dimensionality reduction"
author: "Caroline Akoth"
date: "7/27/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Week 15 Project on Unsupervised Learning

You are a Data analyst at Carrefour Kenya and are currently undertaking a project that will inform the marketing department on the most relevant marketing strategies that will result in the highest no. of sales (total price including tax). Your project has been divided into four parts where you'll explore a recent marketing dataset by performing various unsupervised learning techniques and later providing recommendations based on your insights.

Part 1: Dimensionality Reduction

This section of the project entails reducing your dataset to a low dimensional dataset using the t-SNE algorithm or PCA. You will be required to perform your analysis and provide insights gained from your analysis.

Part 2: Feature Selection

This section requires you to perform feature selection through the use of the unsupervised learning methods learned earlier this week. You will be required to perform your analysis and provide insights on the features that contribute the most information to the dataset.

Part 3: Association Rules

This section will require that you create association rules that will allow you to identify relationships between variables in the dataset. You are provided with a separate dataset that comprises groups of items that will be associated with others. Just like in the other sections, you will also be required to provide insights for your analysis.

Part 4: Anomaly Detection

You have also been requested to check whether there are any anomalies in the given sales dataset. The objective of this task being fraud detection.

```{r Dimensionality reduction}
## Part 1 Dimensionality Reduction

```

## Task
Conduct Analysis for carrefour Kenya to determine best marketing strategies 

# Metric of Success
For Part 1. Conduct dimensionality reduction  through PCA or t-SNE algorithm.


# Experimental Design 

1. Data Cleaning 
  - Identify and Remove/replace  Missing data
  - Identify and remove duplicate values
  - Removing anomalies
  
2.  Exploratory Data Analysis
  - Univariate, Bivariate and Multivariate Analysis
  
3. Dimensionality Reduction 
 -  Association Rules
```{r}
#Load Libraries
library(dplyr)
library(tidyr)
library(ggplot2)
library(pander)
library(forcats)

```
 

```{r Data, echo=FALSE}
# Read Data
part1 <- read.csv("D:/Education/Self Learning/Data Science/R Tutorials/Week 15 Unsupervised/Supermarket_Dataset_1 - Sales Data.csv")

head(part1)

```
#Read column names
```{r}
colnames(part1)
```
#Read Dimensions and Structure of the Data Frame
```{r}
dim(part1)
```
Data has 1000 entries and 16 columns
```{r}
str(part1)
```
Data is made up of 8 Numerical columns and 8 factor columns

```{r}
summary(part1)
```
#Find Missing data
```{r}
is.na(part1)
```
No Missing values
#Find Duplicates

```{r}
duplicated(part1)
```
No duplicated entries in the dataset

# Find outliers
```{r}
boxplot(part1)
```

# Exploratory Data Analysis

#Univariate Plots
```{r}
part1 %>%
    ggplot(aes(Quantity)) +
    geom_histogram(binwidth = 1.25, color = "black",fill = "grey") +
    geom_vline(xintercept = mean(part1$Quantity), lwd = 2) +
    labs(title = "Distribution of Quantity",
         x = "Payment",
         y = "Frequency") +
    theme_minimal() +
    scale_x_continuous(breaks = seq(7.5,35,2.5))
```
# Pie Chart of male vs Female customers
```{r}
pie(table(part1$Gender), main="male vs female")
```
The customers are split at 50 % being male and 50% female

#

```{r}
membership <- table(part1$Customer.type)
barplot(membership,main = "Customer Type",col = topo.colors(2), ylim = c(0,800))
legend("topright",inset = .02, title="Customer Type",
       c("Member","Non Member"), fill=topo.colors(2), cex=0.8)
```

```{r}
branch <- table(part1$Branch)
barplot(branch,main = "Branch Details",col = topo.colors(2), ylim = c(0,800))
legend("topright",inset = .02, title="Branch Details",
       c("A","B","C"), fill=topo.colors(2), cex=0.8)
```

## Bivariate Analysis

```{r}
#install.packages("ggcorrplot")
library(ggcorrplot)
part1 %>%
    select_if(is.numeric) %>%
    cor %>% 
    ggcorrplot()
```

Most variables are not correlated.
```{r}
#check column str again
str(part1)
```

```{r}
num_col <- part1[,c(6,7,8,12,13,14,15,16)]
head(num_col)
```

#Covariance
```{r}
covariance_matrix = cov(num_col)
covariance <-as.data.frame(round(covariance_matrix,2))
```
#Correlation
```{r}
# Correlation Matrix
correlation_matrix = cor(num_col)
corr <- as.data.frame(round(correlation_matrix,2))
corr
```
#Scatter Plots
```{r}
colnames(part1)
```


```{r}
branch <- part1$Branch
unitprice <- part1$Unit.price
gross <- part1$gross.income

plot(branch, unitprice, xlab="Branch",ylab = "Unit Price",main = "Branch vs Unit Price")
plot(gross,unitprice,xlab = "Gross",ylab = "Unit Price",main="Gross pay vs Unit Price")
plot(gross,branch, xlab="Daily Time spent", ylab="Daily Internet Usage",main = "Daily Time Spent on Site vs Daily Internet Usage")

```
## Dimensionality Reduction using PCA

Numerical Variable  = num_col



